---
title: "Assignment_1"
format: pdf
editor: visual
---

#2

\(a\)

$$
E(Y) = y_1p_1+...+y_k+p_k = \sum_{i=1}^ky_ip_i
$$\

\(b\)

$$
\sigma_Y = Var(Y) = E[(Y-\mu_y)^2]=\int_{i=1}^k(y_i-\mu_y)^2p_i
$$\
(c)

$$
\bar{\beta} = \frac{\int_{i=1}^n(y-y_i)(x-x_i)}{\int_{i+1}^n(x-x)^2}
$$\
(d)

$$
P(a\leq Y\leq b) = \int_a^bf_Y(y)dy
$$\
(e)

$$
\hat{g}(x) = \frac{\frac{1}{nh}\int_{i=1}^ny_ik(\frac{x_i-x}{h})}{\frac{1}{nh}\int_{i=1}^nk(\frac{x_i-x}{h})}
$$\
\
\

$$
z_1 = \sqrt{-2ln(\mu_1)} x cos(2\pi\mu_2)
$$\

$$
z_2 = \sqrt{-2ln(\mu_1)} x sin(2\pi\mu_x)
$$\

$$
z = [z_1,z_2]
$$\
\

#3.1

(a) 

```{r}
n = 1000
```

(b) 

```{r}
mu_1 <- runif(n/2,0,1) 
mu_2 <- runif(n/2,0,1)
```

(c) 

```{r}
z_1 <- sqrt(-2*log(mu_1))*cos(2*pi*mu_2)
z_2 <- sqrt(-2*log(mu_1))*sin(2*pi*mu_2)
```

(d) 

```{r}
z <- c(z_1,z_2)
```

(e) 

```{r}
mu=5
sigma=2
```

(f) 

```{r}
x = mu + sigma * z
```

(g) 

```{r}
mean(x)
sd(x)
```

(h) 

```{r}
 hist(x,
 freq= FALSE,
 ylab= "Density",
 xlab= "$x$")

 curve(dnorm(x,mean= mu,sd= sigma),
 col= "red", lwd= 2,add = TRUE)
```

#3.2

```{r}

cihi <- read.csv("hlthexp.csv")

df <- data.frame(Year = cihi$Year,
                 Hospitals = cihi$Hospitals,
                 Physicians = cihi$Physicians,
                 "Other Services" = cihi$Other.Institutions,
                 Dental = cihi$Other.Professionals..Dental.Services,
                 Vision = cihi$Other.Professionals..Vision.Care.Services,
                 "Other Professionals" = cihi$Other.Professionals..Other.Services,
                 check.names = FALSE)
```

(a) Determine if there are any missing values for the variable Hospitals No missing values number of observations is 48 each has a value

```{r}
df$Hospitals
```

(b) 

```{r}
df$total_other_services <- df$Dental+ df$Vision + df$"Other Professionals"
```

(D) 

```{r}
cihi <- data.frame(cihi, "Perscription.Drugs" = "Prescribed.Drugs")
```

\(e\) Using a single R command, determine the expenditure on hospitals in 1983.

```{r}
Expenditure_1983 <- cihi["9", "Hospitals"]

#df$Hospitals[df$Year:1983]

```

\(f\) Using a singe R command, list the expenditures by year for 2012-202

```{r}
df$Hospitals
Expenditure_2012_2022 <- cihi["38-48", "Hospitals"]


```

#3.3

(a) 

```{r}
mpg <- ggplot2::mpg
subset(mpg, year == 2008)
min(mpg$cty)
max(mpg$cty)
```

(b) 

```{r}
n <- 11
avg_mpg = sum(mpg$cty)/n
```

$$ Avg Mpg = \frac{sum_{i-1}^ncty_i}{n}$$

(c) 

```{r}
mean(mpg$cty)
```

(d) 

```{r}
compact <- subset(mpg, class == "compact")
 ifelse(compact == "compact", 1, 0)

 #x <- c(-2, 0, 3)
 #ifelse(x > 0, "Positive", "Not Positive")
#compact <- subset(mpg, class == "compact")  
```

(e) Estimate average miles per gallon within cit limits for compact cars

```{r}
avg_mpg <- mean(compact$cty)
```

(f) Create a Scatter Plot X-axis city mpg (cty) Y-axis highway mpg(hwy)

```{r}
#| eval: true
#| label: fig-1
#| fig-cap:  "City Versus Highway Fuel Efficiency (MPG"

x <- mpg$cty
y <- mpg$hwy

plot(x, 
     y, 
     xlab="City MPG", 
     ylab="Highway MPG")

```

@fig-1 shows the etc.
